### 2010-06-26 paper/IIWAS2010/content/related_work.tex
Modifications to ontology generators section: YAGO

The DBpedia\footnote{http://dbpedia.org} project is based on extracting 
semantic information from the Wikipedia and making it available on the Web. 
Wikipedia semantics includes info-box templates, categorization information, 
images, Geo-coordinates, links to external Web pages, disambiguation pages, 
and redirects between pages in Wiki markup form \cite{Auer07dbpedia:a, Bizer2009}. 
DBpedia represents the Wikipedia categories using skos:concepts and category 
relations using skos:broader \cite{Auer07dbpedia:a, Bizer2009}. In fact, 
DBpedia does not define any new relations between the Wikipedia categories. 
The Wikipedia categories are extracted directly from Wikipedia pages, and there 
is no quality check on the resultant ontology. Similarly, additional ontological 
relations in DBpedia are generated from the info-box attributes and their values.

YAGO is a semi-automatically constructed ontology from Wikipedia and
WordNet\cite{Suchanek2009phd}. The YAGO ontology uses an automated process to
extract information from Wikipedia pages, info-boxes, and categories and to
combine this information with the WordNet\footnote{http://wordnet.princeton.edu}
synsets heterarchy. Since Wikipedia contains more individuals in the form of
Wikipedia pages than in the man-made WordNet ontology, the Wikipedia page titles
are used as the YAGO ontology individuals. YAGO concentrates mainly on the
fields of people, cities, events, and movies\cite{Suchanek2009phd}.

In addition, YAGO uses Wikipedia categories as its ontology classes. The
ontology's heterarchy is built using the \textit{hypernym} and \textit{hyponym}
relations of the WordNet synsets. YAGO uses only the nouns from WordNet and
ignores the WordNet verbs and adjectives. The connection between a WordNet
synset and a Wikipedia category is achieved by parsing the category names and
matching the parsed category components with the WordNet
synsets\cite{Suchanek2009phd}. Those Wikipedia categories having no WordNet
match are ignored in the YAGO ontology.

However, YAGO type extraction is mainly based on the assumption that
each Wikipedia page has at least one tagged category, and the assigned Wikipedia
categories are relevant to that Wikipedia page. The Wikipedia page category
assignments are subjectively assigned by human editors and some Wiki pages are
unassigned i.e., they have no category. In addition, we cannot completely rely
on the relevance of these assigned Wikipedia page categories.

%\subsection{NLP Interfaces}

>>>>

The DBpedia\footnote{http://dbpedia.org} project is based on extracting 
semantic information from the Wikipedia and making it available on the Web. 
Wikipedia semantics includes info-box templates, categorization information, 
images, Geo-coordinates, links to external Web pages, disambiguation pages, 
and redirects between pages in Wiki markup form \cite{Bizer2009}. 
DBpedia represents the Wikipedia categories using skos:concepts and category 
relations using skos:broader \cite{Bizer2009}. In fact, 
DBpedia does not define any new relations between the Wikipedia categories. 
The Wikipedia categories are extracted directly from Wikipedia pages, and there 
is no quality check on the resultant ontology. Similarly, additional ontological 
relations in DBpedia are generated from the info-box attributes and their values.

YAGO is a semi-automatically constructed ontology from the Wikipedia pages, info-boxes, categories and WordNet\footnote{http://wordnet.princeton.edu} synsets heterarchy\cite{Suchanek2009phd}. YAGO uses the Wikipedia page titles as its ontology individuals and categories as its ontology classes. The ontology's heterarchy is built using the \textit{hypernym} and \textit{hyponym} relations of the WordNet synsets. YAGO uses only the nouns from WordNet and ignores the WordNet verbs and adjectives. The connection between a WordNet synset and a Wikipedia category is achieved by parsing the category names and matching the parsed category components with the WordNet synsets\cite{Suchanek2009phd}. Those Wikipedia categories having no WordNet match are ignored in the YAGO ontology.

However, YAGO type extraction assumes that each Wikipedia page has at least one tagged category, and the assigned Wikipedia categories are relevant to that Wikipedia page. The Wikipedia page category assignments are subjectively assigned by human editors and some Wiki pages are unassigned i.e., they have no category. In addition, we cannot fully rely on the relevance of these assigned Wikipedia page categories. In addition, YAGO concentrates mainly on the fields of people, cities, events, and movies\cite{Suchanek2009phd}.
